---
title: "How to measure resilience when there is no demand?"
author: "Rainer Koelle, EUROCONTROL, Brussels (Belgium) Fabio Barbosa, DECEA, Rio de Janeiro (Brazil)"
#date: "04/03/2022"
output: 
  bookdown::word_document2: 
    reference_docx: "_template-22AuthorsInst.docx"
bibliography: "_resilience.bib"
#  abstract: |    ICNS uses heading for abtract
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

Resilience is important.

# Introduction

Teaser

Why important

Previous work

## heading 2

some cool text etc

* bullet 
* more bullets
* one more bullet

### heading 3

cool text and cool reference @koelle_resilience_2015.

possibly some code chunks

```{r}
# this could be code
```

<!-- MOVE THIS AFER THE REFERENCES IN THE FINAL VERSION! -->
# Acknowledgements
If an acknowledgement is necessary, include it under the heading Acknowledgements using the Heading 1 style. Use the Body Text style and include the acknowledgements immediately after the references.
# Disclaimer
If a disclaimer is necessary, include it under the heading Disclaimer using the Heading 1 style. Use the Body Text/Normal Text style and include the disclaimer immediately after the acknowledgements.
# Email Addresses

# Conference Identification

2022 Integrated Communications Navigation and Surveillance (ICNS) Conference
April 5-7, 2022 



# References

